### 2021-12-11 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@9e9861285e5f075d258bb016ab6a58430c5ff49d 🚀

In addition to the literature on SDMs, most of the research on machine
learning application to life sciences is focused on genomics (which has
very specific challenges, see a recent discussion by Whalen et al.,
2021); this sub-field has generated largely different recommendations.
Chicco \& Jurman (2020) suggest using Matthews correlation coefficient
(MCC) over \(F_1\), as a protection against over-inflation of predicted
results; Delgado \& Tibau (2019) advocate against the use of Cohen's
\(\kappa\), again in favor of MCC, as the relative nature of \(\kappa\)
means that a worse classifier can be picked over a better one;
similarly, Boughorbel et al. (2017) recommend MCC over other measures of
performance for imbalanced data, as it has more desirable statistical
properties. More recently, Chicco et al. (2021) temper the apparent
supremacy of the MCC, by suggesting it should be replaced by Youden's
informedness (also known as \(J\), bookmaker's accuracy, and the
True-Skill Statistic) when the imbalance in the dataset may not be
representative (Jordano, 2016a, which is the case as networks are
under-sampled; 2016b; McLeod et al., 2021), when classifiers need to be
compared across different datasets, and when comparing the results to a
no-skill (baseline) classifier is important. As these conditions are
likely to be met with network data, there is a need to evaluate which
measures of classification accuracy respond in a desirable way.

A lot of binary classifiers are built by using a regressor (whose task
is to guess the value of the interaction, amd can therefore return
somethins considered to be a pseudo-probability); in this case, the
optimal value below which predicitions are assumed to be negative
(\emph{i.e.} the interaction does not exist) can be determined by
picking a threshold maximizing some value on the ROC curve or the PR
curve. The area under these curves (ROC-AUC and PR-AUC henceforth) give
ideas on the overall goodness of the classifier. Saito \& Rehmsmeier
(2015) established that the ROC-AUC is biased towards over-estimating
performance for imbalanced data.

>>>>

In addition to the literature on SDMs, most of the research on machine
learning application to life sciences is focused on genomics (which has
very specific challenges, see a recent discussion by Whalen et al.,
2021); this sub-field has generated largely different recommendations.
Chicco \& Jurman (2020) suggest using Matthews correlation coefficient
(MCC) over \(F_1\), as a protection against over-inflation of predicted
results; Delgado \& Tibau (2019) advocate against the use of Cohen's
\(\kappa\), again in favor of MCC, as the relative nature of \(\kappa\)
means that a worse classifier can be picked over a better one;
similarly, Boughorbel et al. (2017) recommend MCC over other measures of
performance for imbalanced data, as it has more desirable statistical
properties. More recently, Chicco et al. (2021) temper the apparent
supremacy of the MCC, by suggesting it should be replaced by Youden's
informedness (also known as \(J\), bookmaker's accuracy, and the
True-Skill Statistic) when the imbalance in the dataset may not be
representative (Jordano, 2016a, which is the case as networks are
under-sampled; 2016b), when classifiers need to be compared across
different datasets (for example when predicting a system in space, where
undersampling varies locally; McLeod et al., 2021), and when comparing
the results to a no-skill (baseline) classifier is important. As these
conditions are likely to be met with network data, there is a need to
evaluate which measures of classification accuracy respond in a
desirable way.

A lot of binary classifiers are built by using a regressor (whose task
is to guess the value of the interaction, amd can therefore return
somethins considered to be a pseudo-probability); in this case, the
optimal value below which predicitions are assumed to be negative
(\emph{i.e.} the interaction does not exist) can be determined by
picking a threshold maximizing some value on the ROC curve or the PR
curve. The area under these curves (ROC-AUC and PR-AUC henceforth) give
ideas on the overall goodness of the classifier. Saito \& Rehmsmeier
(2015) established that the ROC-AUC is biased towards over-estimating
performance for imbalanced data; on the contrary, the PR-AUC is able to
identify classifiers that are less able to detect positive interactions
correctly, with the additional advantage of having a baseline value
equal to prevalence. Therefore, it is important to assess whether these
two measures return different results when applied to ecological network
prediction.
